Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-13 Scripts/Initial_Analysis.Rmd
double checked coordenates

# Test coords

maptest <- ggplot() +
  geom_sf(data = SAU_eez_sf, aes(), fill = NA) +
  geom_point(data = coords,
             aes(
               x = longitude,
               y = latitude
             )
  )

ggsave("maptest.png",
       plot = maptest,
       width = 10,
       height = 8,
       units = "in"
       )

>>>>

# Double check coords
# Note that Australia and Ggreenland have points in the middle of the country because of the EEZ shape

coords_map <- ggplot() +
  geom_sf(data = SAU_eez_sf, aes(), fill = NA) +
  geom_point(data = eez_centroid,
             aes(
               x = longitude,
               y = latitude
             )
  )

ggsave("coords_map.png",
       plot = coords_map,
       width = 10,
       height = 8,
       units = "in"
       )
